Robust calibration of numerical models based on relative regret

### 2019-11-26 article.tex
fix typos, format of recap table, change subscript maxratio to ratio

Numerical models are widely used to study or forecast natural phenomenon and improve industrial processes. However, by essence models only partially represents reality and sources of uncertainties are ubiquitous (discretisation errors, missing physical processes, poorly known boundary conditions).
%Many physical phenomena are modelled numerically in order to better understand and/or to predict their behaviour. Because of the complexity and or ignorance of the underlying physics, numerical models are imperfect representations of the reality. 
%
%Various sources of uncertainties can corrupt the model quality, such as the discretisation of the domain, or presence of  small scale phenomena that can not be fully represented. 
Moreover, such uncertainties may be of different nature. 
~\cite{walker_defining_2003} propose two to consider two categories of uncertainties. On the one hand aleatoric uncertainties,  coming from the inherent variability of a phenomenon, e.g.\ intrinsic randomness of some environmental variables. On the other hand, epistemic uncertainties coming from a lack of knowledge about the properties and conditions of the phenomena underlying the behaviour of the system under study.
The latter can be accounted for through the introduction of ad-hoc correcting terms in the numerical model, that need to be properly estimated. Thus, reducing the epistemic uncertainty can be done through parameters estimation approaches. 
%when one is having observations of the reality. 
This is usually done using optimal control techniques, leading to an optimisation of a well chosen cost function which is typically built as a comparison with reference observations.
%
An application of such an approach, in the context of ocean circulation modeling, is the estimation of ocean bottom friction parameters in~\cite{das_estimation_1991} and~\cite{boutet_estimation_2015}.

@@

Another possibility is to combine directly $p$ and $\checkap$ in order to find a compromise. We opted to model this compromise by the ratio $(p/\checkap)$, as it increases with respect to $p$ and decreases with respect to $\checka_p$. The level of confidence $p_{\mathrm{maxratio}}$ is then defined as the maximiser of $p\mapsto p / \checka_p$.

@@

\begin{table}[t]
  \centering
\begin{tabular}{lrr}
  \toprule
  Definition & Related quantities & Interpretation \\ \midrule
   $\argmin_{\mathbf{k}\in\Kspace} \Ex_{\mathbf{U}}\left[J(\mathbf{k},\mathbf{U})\right]$& $\kmean$ & Long run performances\\
   $\argmin_{\mathbf{k}\in\Kspace} \Var_{\mathbf{U}}\left[J(\mathbf{k},\mathbf{U})\right]$& $\kvar$  & Steady performances\\
   $\argmax_{\mathbf{k}\in\Kspace} p_{\mathbf{K}^*}(\mathbf{k})$ & $\kmpe$ & Most probable minimiser\\
    $\inf\left\{ \alpha \mid \exists \checkkp \in \Kspace,\, \Gamma_{\alpha}(\checkkp) \geq p \right\}$ & $(p, \checkkp,\checkap)$ & Acceptable values with fixed probability $p$ \\
    $p_{\mathrm{maxratio}} = \argmax p/\checkap$ & $(p_{\mathrm{maxratio}}, \checkk_{\mathrm{maxratio}}, \checka_{\mathrm{maxratio}})$ & Maximal ratio of $p$ and $\checkap$ \\
  \bottomrule
\end{tabular}
\label{tab:RO_recap}
  \caption{Robust estimators, based on a cost function $J$}
\end{table}

@@

\begin{table*}[!ht]
\centering
\caption{Estimation performed for $J_{\mathrm{BH}}$, sorted by value}
\label{tab:recap_estimates_branin}
\begin{tabular}{lr}
\toprule
Estimate & Value \\ \midrule
$\hatkvar$ & 1.371 \\ 
$\kest_p,~p=1$ & 1.557 \\ 
$\hatkmean$ & 1.587 \\ 
  $\hatkmpe$ & 1.628 \\
  $\kest_{\mathrm{maxratio}},~\hat{p}_{\mathrm{maxratio}}=0.654$ & 1.637 \\
$\kest_p,~p=0.95$ & 1.672 \\ \bottomrule
\end{tabular}
\end{table*}

@@

\begin{figure*}[t]
  \centering
\includegraphics[width=10cm]{Figures/profile_BH_all_estimates_noku.pdf}
\caption{Profiles of the different estimates for the $J_{\mathrm{BH}}$ function, corresponding to the vertical cross sections of the contour. The shaded region corresponds to the interval $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$. The red dashed line, corresponding to the values taken by the cost function when the control variable is set to $\mathbf{k}_1$, is always between $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$ per design.}
\label{fig:profiles_branin}
\end{figure*}

@@

Compared to the plots for $J_{\mathrm{BH}}$ in Figure~\ref{fig:ratio_BH}, $\hat{\checka}_p$ exhibits a smoother behaviour for the $J_{\mathrm{BHswap}}$ function as no change of slope is easily discernable. The computation of the ratio advocates for a level of confidence $p_{\mathrm{maxratio}}$ close to $0.75$. The numerical values of the estimations $\hat{k}$ presented in Table~\ref{tab:recap_estimates_BHs} show that, contrary to the $J_{\mathrm{BH}}$ function, the objective are concurrent.

\begin{table*}[!h]
\centering
\caption{Estimations performed for $J_{\mathrm{BHswap}}$, sorted by value}
\label{tab:recap_estimates_BHs}
\begin{tabular}{lr} \toprule
Estimate & Value \\ \midrule
$\kest_{\mathrm{MPE}}$ & 0.606 \\ 
$\kest_{\mathrm{maxratio}},~ \hat{p}_{\mathrm{maxratio}}=0.766$ & 1.537 \\ 
$\hatkmean$ & 1.752 \\ 
$\kest_p,~p=0.90$ & 2.112 \\ 
$\kest_p,~p=0.95$ & 2.457 \\ 
$\hatkvar$ & 2.638 \\ 
$\kest_1,~p=1$ & 2.798   \\ \bottomrule
\end{tabular}
\end{table*}

@@

In this case, $\hatkmpe$, $\hatkmean$ and $\hat{\checkk}_{\mathrm{maxratio}}$ present a similar behaviour. They perform very well for $\mathbf{u}>2$, especially for $\hatkmpe$ which is very close to the minimal value; However for $\mathbf{u}<2$, they produce high values of the function.

@@

\begin{figure*}[t]
  \centering
\includegraphics[width=10cm]{Figures/profile_BHs_all_estimates_noku.pdf}
\caption{Profiles of the different estimates for the $J_{\mathrm{BHswap}}$ function. Those profiles are the vertical cross sections of the contours above. The shaded region corresponds to the interval $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$. The red dashed line, corresponding to the values taken by the cost function when the control variable is set to $\mathbf{k}_1$, is always between $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$ per design.}
\label{fig:profiles_branin_switch}
\end{figure*}

@@

The calibration of this numerical model is done in order to get a calibrated value $\kest$, that will be used for forecasts, using the same numerical model. We are now going to compare how well three of those values compare in a forecast context: $\kest_1$, $\hatkmean$ and $\kest_{\mathrm{global}}$, as the first two refer quite naturally to the notion of robustness, and the latter is an example of an estimate that does not take into account the uncertainties.
\clearpage
\subsection{Assessing the quality of the forecast of the calibrated model}
The calibration of the model has been performed using by integrating the model on a time-period $[0, T]$, called assimilation window. 
We now want to compare the quality of the different forecasts, from different calibrated bottom friction.
Those forecasts result from the integration of the numerical model between the time $T$ and a time $T_{\mathrm{pred}}$.
Given the probabilistic nature of the environmental conditions $\mathbf{U}$, the forecasts will also be probabilistic. We will then compare $\mathcal{M}_{\mathrm{pred}}^o(\mathbf{U})$ and $\mathcal{M}_{\mathrm{pred}}(\mathbf{k},\mathbf{U})$, for a calibrated $\mathbf{k}$. The metric of comparison will be the squared forecast error, and the Continuous Ranked Probability Score (CRPS). The calibrated values that are compared are the minimiser of the expectation $\hatkmean$, the minimiser of the variance $\hatkvar$, the relative regret of level $p=1$: $\kest_1$ as described in the previous section, but also the global minimiser $\kest_{\mathrm{global}}$, and some conditional minimisers $\kest^*(\mathbf{u}^i)$ where the chosen environmental variables are $\{\mathbf{u}^i\}_{1\leq i \leq 4} = \{0.5, 0.55, 0.65, 0.7\}$. $\kest^*(0.6)$ has been omitted due to the fact that it result in a value very similar to the minimum of the expectation. These have been included in order to compare the different metrics obtained without using a robust approach. \todo{à revoir}

\subsubsection{Squared forecast error}
Given two environmental conditions $\mathbf{u}$, used to run the computer simulation and $\mathbf{u}'$, used to generate the observations, the squared forecast error for the parameter $\mathbf{k}$ is
\begin{equation}
\label{eq:squared_forecast_error}
S_{\mathrm{pred}}(\mathbf{k},\mathbf{u},\mathbf{u}') = \left(\mathcal{M}_{\mathrm{pred}}(\mathbf{k},\mathbf{u}) - \mathcal{M}^{o}_{\mathrm{pred}}(\mathbf{u}')\right)^2
\end{equation}
Averaging over $\mathbf{u}$, $\mathbf{u}'$ defines the mean squared forecast error, defined on every point of the spatial domain, and at every time-steps. This can be done using a Monte-Carlo approximation: as $\mathbf{u}$ and $\mathbf{u}'$ are iid, let us assume that we have a set of samples $\{\mathbf{u}^i\}_{1\leq i \leq N_{\mathbf{u}}}$. The squared forecast error can then be approximated using this finite set of samples:
\begin{equation}
  \label{eq:squared_forecast_error_averaged}
  S(\mathbf{k}) = \frac{1}{N_{\mathbf{u}}^2 }\sum_{i=1}^{N_{\mathbf{u}}}\sum_{j=1}^{N_{\mathbf{u}}} S_{\mathrm{pred}}(\mathbf{k},\mathbf{u}^i,\mathbf{u}^j) = \frac{1}{N_{\mathbf{u}}^2 }\sum_{i=1}^{N_{\mathbf{u}}}\sum_{j=1}^{N_{\mathbf{u}}}  \left(\mathcal{M}_{\mathrm{pred}}(\mathbf{k},\mathbf{u}^i) - \mathcal{M}^{o}_{\mathrm{pred}}(\mathbf{u}^j)\right)^2
\end{equation}
The mean squared forecast error averaged over the whole space and over all the time-steps gives an indication on the overall prediction quality of the prediction given this metric, and are represented on the right plot of Figure~\ref{fig:forecast_squared_error}. We can see that $\kest_{\mathrm{global}}$ performs slightly better than $\kest_1$, itself performing slightly better than $\hatkmean$.
Averaging $S(\mathbf{\kest})$ over the time steps between $T$ and $T_{\mathrm{pred}}$, we have an indication on the quality of the forecast in the squared sense depending on the spatial position, as seen on the left plot of Figure~\ref{fig:forecast_squared_error}.
\begin{figure*}[!h]
\centering
\includegraphics[width=.9\textwidth]{Figures/L2_full.pdf}
\caption{Quality of forecast, depending on the calibrated parameter. The left figures show the metric averaged over time, while the right figure show the mean forecast error, averaged over time and space}
\label{fig:forecast_squared_error}
\end{figure*}
We can see that the mean forecast error squared, on the right side, averaged over time and space is the smallest for $\kest_{\mathrm{global}}$, while $\kest_{1.0}$ performs slightly better $\hatkmean$.

% \begin{figure*}[!h]
% \centering
% \includegraphics[width=10cm]{Figures/distrib_L2norm.pdf}
% \caption{Distribution of the forecast squared error, averaged over the different values of the uncertain parameter in the numerical simulations \victor{doublon avec fig.\ref{fig:forecast_squared_error} ?}}
% \label{fig:forecast_squared_error_distrib}
% \end{figure*}
One issue with the squared forecast error is that it will penalize strongly a high sensitivity to the environmental conditions \todo{à conserver/changer ?}. A way to deal with this is to use another metric, that takes the probabilistic nature of the forecasts into account.
\subsubsection{Continuous Ranked Probability Score}
Given the random variables $\mathcal{M}_{\mathrm{pred}}(\kest, \mathbf{U})$ and $\mathcal{M}_{\mathrm{pred}}^o(\mathbf{U})$, representing the probabilistic forecast and the probabilistic observations, we can define the cumulative distribution functions (CDF) $F_{\mathrm{pred}}(\cdot, \kest)$ and $F^o_{\mathrm{pred}}(\cdot)$
The Continuous ranked probability score (CRPS) measures the squared difference between the predicted CDF $F_{\mathrm{pred}}$ using a calibrated value, and the CDF of the observations $F_{\mathrm{pred}}^o$. 
\begin{equation}
\label{eq:def_crps}
\mathrm{CRPS}(\mathbf{k}) = \int_{\mathbb{R}} (F_{\mathrm{pred}}(x,\mathbf{k}) - F^o_{\mathrm{pred}}(x))^2 \,\mathrm{d}x
\end{equation}

\begin{figure}[!h]
  \centering
  \includegraphics[width=.9\textwidth]{Figures/CRPS_full}
  \caption{CRPS computed for different calibrated parameters}
\label{fig:forecast_crps}
\end{figure}

\clearpage
\section*{Conclusion}  
\victor{À faire à la fin}
This paper deals with the problem of robust calibration of a computer code in the presence of uncertain inputs.

>>>>

Numerical models are widely used to study or forecast natural phenomenon and improve industrial processes. However, by essence models only partially represents reality and sources of uncertainties are ubiquitous (discretisation errors, missing physical processes, poorly known boundary conditions).
%Many physical phenomena are modelled numerically in order to better understand and/or to predict their behaviour. Because of the complexity and or ignorance of the underlying physics, numerical models are imperfect representations of the reality. 
%
%Various sources of uncertainties can corrupt the model quality, such as the discretisation of the domain, or presence of  small scale phenomena that can not be fully represented. 
Moreover, such uncertainties may be of different nature. 
~\cite{walker_defining_2003} proposes to consider two categories of uncertainties. On the one hand aleatoric uncertainties,  coming from the inherent variability of a phenomenon, e.g.\ intrinsic randomness of some environmental variables. On the other hand, epistemic uncertainties coming from a lack of knowledge about the properties and conditions of the phenomena underlying the behaviour of the system under study.
The latter can be accounted for through the introduction of ad-hoc correcting terms in the numerical model, that need to be properly estimated. Thus, reducing the epistemic uncertainty can be done through parameters estimation approaches. 
%when one is having observations of the reality. 
This is usually done using optimal control techniques, leading to an optimisation of a well chosen cost function which is typically built as a comparison with reference observations.
%
An application of such an approach, in the context of ocean circulation modeling, is the estimation of ocean bottom friction parameters in~\cite{das_estimation_1991} and~\cite{boutet_estimation_2015}.

@@

Another possibility is to combine directly $p$ and $\checkap$ in order to find a compromise. We opted to model this compromise by the ratio $(p/\checkap)$, as it increases with respect to $p$ and decreases with respect to $\checka_p$. The level of confidence $p_{\mathrm{ratio}}$ is then defined as the maximiser of $p\mapsto p / \checka_p$.

@@

\begin{table}[t]
  \centering
\begin{tabular}{lrp{5cm}}
  \toprule
  Definition & Related quantities & Interpretation \\ \midrule
   $\argmin_{\mathbf{k}\in\Kspace} \Ex_{\mathbf{U}}\left[J(\mathbf{k},\mathbf{U})\right]$& $\kmean$ & Long run performances\\
   $\argmin_{\mathbf{k}\in\Kspace} \Var_{\mathbf{U}}\left[J(\mathbf{k},\mathbf{U})\right]$& $\kvar$  & Steady performances\\
   $\argmax_{\mathbf{k}\in\Kspace} p_{\mathbf{K}^*}(\mathbf{k})$ & $\kmpe$ & Most probable minimiser\\
    $\inf\left\{ \alpha \mid \exists \checkkp \in \Kspace,\, \Gamma_{\alpha}(\checkkp) \geq p \right\}$ & $(p, \checkkp,\checkap)$ & Acceptable values\newline with fixed probability $p$ \\
    $p_{\mathrm{ratio}} = \argmax p/\checkap$ & $(p_{\mathrm{ratio}}, \checkk_{\mathrm{ratio}}, \checka_{\mathrm{ratio}})$ & Maximal ratio of $p$ and $\checkap$ \\
  \bottomrule
\end{tabular}
\label{tab:RO_recap}
  \caption{Robust estimators, based on a cost function $J$}
\end{table}

@@

\begin{table*}[!ht]
\centering
\caption{Estimation performed for $J_{\mathrm{BH}}$, sorted by value}
\label{tab:recap_estimates_branin}
\begin{tabular}{lr}
\toprule
Estimate & Value \\ \midrule
$\hatkvar$ & 1.371 \\ 
$\kest_p,~p=1$ & 1.557 \\ 
$\hatkmean$ & 1.587 \\ 
  $\hatkmpe$ & 1.628 \\
  $\kest_{\mathrm{ratio}},~\hat{p}_{\mathrm{ratio}}=0.654$ & 1.637 \\
$\kest_p,~p=0.95$ & 1.672 \\ \bottomrule
\end{tabular}
\end{table*}

@@

\begin{figure*}[!h]
  \centering
\includegraphics[width=10cm]{Figures/profile_BH_all_estimates_noku.pdf}
\caption{Profiles of the different estimates for the $J_{\mathrm{BH}}$ function, corresponding to the vertical cross sections of the contour. The shaded region corresponds to the interval $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$. The red dashed line, corresponding to the values taken by the cost function when the control variable is set to $\mathbf{k}_1$, is always between $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$ per design.}
\label{fig:profiles_branin}
\end{figure*}

@@

Compared to the plots for $J_{\mathrm{BH}}$ in Figure~\ref{fig:ratio_BH}, $\hat{\checka}_p$ exhibits a smoother behaviour for the $J_{\mathrm{BHswap}}$ function as no change of slope is easily discernable. The computation of the ratio advocates for a level of confidence $p_{\mathrm{ratio}}$ close to $0.75$. The numerical values of the estimations $\hat{k}$ presented in Table~\ref{tab:recap_estimates_BHs} show that, contrary to the $J_{\mathrm{BH}}$ function, the objective are concurrent.

\begin{table*}[!h]
\centering
\caption{Estimations performed for $J_{\mathrm{BHswap}}$, sorted by value}
\label{tab:recap_estimates_BHs}
\begin{tabular}{lr} \toprule
Estimate & Value \\ \midrule
$\kest_{\mathrm{MPE}}$ & 0.606 \\ 
$\kest_{\mathrm{ratio}},~ \hat{p}_{\mathrm{ratio}}=0.766$ & 1.537 \\ 
$\hatkmean$ & 1.752 \\ 
$\kest_p,~p=0.90$ & 2.112 \\ 
$\kest_p,~p=0.95$ & 2.457 \\ 
$\hatkvar$ & 2.638 \\ 
$\kest_1,~p=1$ & 2.798   \\ \bottomrule
\end{tabular}
\end{table*}

@@

In this case, $\hatkmpe$, $\hatkmean$ and $\hat{\checkk}_{\mathrm{ratio}}$ present a similar behaviour. They perform very well for $\mathbf{u}>2$, especially for $\hatkmpe$ which is very close to the minimal value; However for $\mathbf{u}<2$, they produce high values of the function.

@@

\begin{figure*}[!h]
  \centering
\includegraphics[width=10cm]{Figures/profile_BHs_all_estimates_noku.pdf}
\caption{Profiles of the different estimates for the $J_{\mathrm{BHswap}}$ function. Those profiles are the vertical cross sections of the contours above. The shaded region corresponds to the interval $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$. The red dashed line, corresponding to the values taken by the cost function when the control variable is set to $\mathbf{k}_1$, is always between $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$ per design.}
\label{fig:profiles_branin_switch}
\end{figure*}

@@

The calibration of this numerical model is done in order to get a calibrated value $\kest$, that will be used for forecasts, using the same numerical model. We are now going to compare how well three of those values compare in a forecast context: $\kest_1$, $\hatkmean$ and $\kest_{\mathrm{global}}$, as the first two refer quite naturally to the notion of robustness, and the latter is an example of an estimate that does not take into account the uncertainties.

\subsection{Assessing the quality of the forecast of the calibrated model}
The calibration of the model has been performed using by integrating the model on a time-period $[0, T]$, called assimilation window. 
We now want to compare the quality of the different forecasts, from different calibrated bottom friction.
Those forecasts result from the integration of the numerical model between the time $T$ and a time $T_{\mathrm{pred}}$.
Given the probabilistic nature of the environmental conditions $\mathbf{U}$, the forecasts will also be probabilistic. We will then compare $\mathcal{M}_{\mathrm{pred}}^o(\mathbf{U})$ and $\mathcal{M}_{\mathrm{pred}}(\mathbf{k},\mathbf{U})$, for a calibrated $\mathbf{k}$. The metric of comparison will be the squared forecast error, and the Continuous Ranked Probability Score (CRPS). The calibrated values that are compared are the minimiser of the expectation $\hatkmean$, the minimiser of the variance $\hatkvar$, the relative regret of level $p=1$: $\kest_1$ as described in the previous section, but also the global minimiser $\kest_{\mathrm{global}}$, and some conditional minimisers $\kest^*(\mathbf{u}^i)$ where the chosen environmental variables are $\{\mathbf{u}^i\}_{1\leq i \leq 4} = \{0.5, 0.55, 0.65, 0.7\}$. $\kest^*(0.6)$ has been omitted due to the fact that it result in a value very similar to the minimum of the expectation. These have been included in order to compare the different metrics obtained without using a robust approach. \todo{à revoir}

\subsubsection{Squared forecast error}
Given two environmental conditions $\mathbf{u}$, used to run the computer simulation and $\mathbf{u}'$, used to generate the observations, the squared forecast error for the parameter $\mathbf{k}$ is
\begin{equation}
\label{eq:squared_forecast_error}
S_{\mathrm{pred}}(\mathbf{k},\mathbf{u},\mathbf{u}') = \left(\mathcal{M}_{\mathrm{pred}}(\mathbf{k},\mathbf{u}) - \mathcal{M}^{o}_{\mathrm{pred}}(\mathbf{u}')\right)^2
\end{equation}
Averaging over $\mathbf{u}$, $\mathbf{u}'$ defines the mean squared forecast error, defined on every point of the spatial domain, and at every time-steps. This can be done using a Monte-Carlo approximation: as $\mathbf{u}$ and $\mathbf{u}'$ are iid, let us assume that we have a set of samples $\{\mathbf{u}^i\}_{1\leq i \leq N_{\mathbf{u}}}$. The squared forecast error can then be approximated using this finite set of samples:
\begin{equation}
  \label{eq:squared_forecast_error_averaged}
  S(\mathbf{k}) = \frac{1}{N_{\mathbf{u}}^2 }\sum_{i=1}^{N_{\mathbf{u}}}\sum_{j=1}^{N_{\mathbf{u}}} S_{\mathrm{pred}}(\mathbf{k},\mathbf{u}^i,\mathbf{u}^j) = \frac{1}{N_{\mathbf{u}}^2 }\sum_{i=1}^{N_{\mathbf{u}}}\sum_{j=1}^{N_{\mathbf{u}}}  \left(\mathcal{M}_{\mathrm{pred}}(\mathbf{k},\mathbf{u}^i) - \mathcal{M}^{o}_{\mathrm{pred}}(\mathbf{u}^j)\right)^2
\end{equation}
The mean squared forecast error averaged over the whole space and over all the time-steps gives an indication on the overall prediction quality of the prediction given this metric, and are represented on the right plot of Figure~\ref{fig:forecast_squared_error}. We can see that $\kest_{\mathrm{global}}$ performs slightly better than $\kest_1$, itself performing slightly better than $\hatkmean$.
Averaging $S(\mathbf{\kest})$ over the time steps between $T$ and $T_{\mathrm{pred}}$, we have an indication on the quality of the forecast in the squared sense depending on the spatial position, as seen on the left plot of Figure~\ref{fig:forecast_squared_error}.
\begin{figure*}[!h]
\centering
\includegraphics[width=.9\textwidth]{Figures/L2_full.pdf}
\caption{Squared forecast error, depending on the calibrated parameter. The left figures show the metric averaged over time, while the right figure show the mean forecast error, averaged over time and space}
\label{fig:forecast_squared_error}
\end{figure*}
We can see that the mean forecast error squared, on the right side, averaged over time and space is the smallest for $\kest_{\mathrm{global}}$, while $\kest_{1.0}$ performs slightly better $\hatkmean$.

One issue with the squared forecast error is that it will penalize strongly a high sensitivity to the environmental conditions \todo{à conserver/changer ?}. A way to deal with this is to use another metric, that takes the probabilistic nature of the forecasts into account.
\subsubsection{Continuous Ranked Probability Score}
Given the random variables $\mathcal{M}_{\mathrm{pred}}(\kest, \mathbf{U})$ and $\mathcal{M}_{\mathrm{pred}}^o(\mathbf{U})$, representing the probabilistic forecast and the probabilistic observations, we can define the cumulative distribution functions (CDF) $F_{\mathrm{pred}}(\cdot, \kest)$ and $F^o_{\mathrm{pred}}(\cdot)$
The Continuous ranked probability score (CRPS) measures the squared difference between the predicted CDF $F_{\mathrm{pred}}$ using a calibrated value, and the CDF of the observations $F_{\mathrm{pred}}^o$. 
\begin{equation}
\label{eq:def_crps}
\mathrm{CRPS}(\mathbf{k}) = \int_{\mathbb{R}} (F_{\mathrm{pred}}(x,\mathbf{k}) - F^o_{\mathrm{pred}}(x))^2 \,\mathrm{d}x
\end{equation}
The left plot of Figure~\ref{fig:forecast_crps} shows the CRPS averaged over time, and the right plot shows the value of the CRPS averaged over time and space. The difference between the squared forecast error and the CRPS is apparent when comparing the general trends shared by the different calibrated parameters. According to the squared error, the region around $x=4$ is not well predicted, while around $x=8$, the prediction are better. On the other hand, according to the CRPS, the region around $x=8$ provide worse forecasts than the one at $x=4$ and $x=7$.

\begin{figure}[!h]
  \centering
  \includegraphics[width=.9\textwidth]{Figures/CRPS_full}
  \caption{CRPS computed for different calibrated parameters}
\label{fig:forecast_crps}
\end{figure}
The numerical evaluations of the CRPS for different parameters show the same order of performances observed for the squared error.
The calibrated parameters that present the best performances for forecasts according to those two metrics are $\kest^*(0.7)$, $\kest^*(0.65)$ which is very similar to $\kest_{\mathrm{global}}$.

\clearpage

\section*{Conclusion}  
\victor{À faire à la fin}
This paper deals with the problem of robust calibration of a computer code in the presence of uncertain inputs.
